MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
little code styling revision

#further analysis
#select distance data from 2 points shot scored and the players who scored it
distance2 <- c()
players2 <- c()
for (z in 1:nrow(df)){
  if(df[z, "SHOT_RESULT"] == 1 & df[z, "PTS_TYPE"] == 2){
    distance2 <- c(distance2, df[z, "CLOSE_DEF_DIST"])
    players2 <- c(players2, as.character(df[z, "player_name"]))
  }
}

>>>>

#Further analysis
#select distance data from 2 points shot scored and the players who scored it
distance2 <- c()
players2 <- c()
for (z in 1:nrow(df)){
  if(df[z, "SHOT_RESULT"] == 1 & df[z, "PTS_TYPE"] == 2){
    distance2 <- c(distance2, df[z, "CLOSE_DEF_DIST"])
    players2 <- c(players2, as.character(df[z, "player_name"]))
  }
}
